A Parallel, Backjumping Subgraph Isomorphism Algorithm using Supplemental Graphs

### 2015-06-22 paper/paper.tex
Ordering

\Cref{algorithm:search} describes our recursive search procedure. If every variable has already been
assigned, we succeed (\lineref{line:success}). Otherwise, we pick a variable (\lineref{line:branch})
to branch on by selecting the variable with smallest domain, tiebreaking on static degree only in
the original pattern graph (we tried other variations, including using supplemental graphs for
calculating degree, and domain over degree, but none gave an overall improvement).  For each value
in its domain in turn, ordered by static degree in the target graph \cite{Geelen:1992}, we try
assigning that value to the variable (\lineref{line:assign}). If we do not detect a failure, we
recurse (\lineref{line:recursesearch}).

>>>>

\Cref{algorithm:search} describes our recursive search procedure. If every variable has already been
assigned, we succeed (\lineref{line:success}). Otherwise, we pick a variable (\lineref{line:branch})
to branch on by selecting the variable with smallest domain, tiebreaking on descending static degree only in
the original pattern graph (we tried other variations, including using supplemental graphs for
calculating degree, and domain over degree, but none gave an overall improvement).  For each value
in its domain in turn, ordered by descending static degree in the target graph \cite{Geelen:1992},
we try assigning that value to the variable (\lineref{line:assign}). If we do not detect a failure,
we recurse (\lineref{line:recursesearch}).
